Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-01 Latex/journal_v1/V4/pr.tex
latex

In addition, there are $R$ multi-antenna o-RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of o-RUs.
Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not. Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

>>>>

In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
Moreover, all O-RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not. Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
